Verifying synchronous distributed algorithms using IVy

### 2018-08-12 paper/paper.tex
- page 3, section (II.ii): "... the language through which *the behavior of* 	the algorithm is defined"
- page 3, section (II.ii.4): "*For example, * this line 	non-deterministically..."

\subsection{The IVy language}
The IVy language is a core part of the IVy system. It is the language through which the algorithm to be verified is defined.
This section presents a selection of core language features that should help the reader understand the paradigm of modelling in IVy, as well as lay the necessary foundation to understand
the rest of the work presented in this paper. This section oversimplifies and does not give an exhaustive documentation, which is given in \cite{refLanguageDoc}.

@@

\subsubsection{Non deterministic choice}
To non-deterministically assign to a variable, relation or function ``*'' is used.
This line non-deterministically chooses a number of nodes to have failed.

>>>>

\subsection{The IVy language}
The IVy language is a core part of the IVy system. It is the language through which the behaviour of the algorithm to be verified is defined.
This section presents a selection of core language features that should help the reader understand the paradigm of modelling in IVy, as well as lay the necessary foundation to understand
the rest of the work presented in this paper. This section oversimplifies and does not give an exhaustive documentation, which is given in \cite{refLanguageDoc}.

@@

\subsubsection{Non deterministic choice}
To non-deterministically assign to a variable, relation or function ``*'' is used.
For example, this line non-deterministically chooses a number of nodes to have failed.
